---
title: "tarprof"
vignette: >
  %\VignetteIndexEntry{tarprof}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
output:
  html_vignette:
    df_print: paged
  html_document:
    df_print: paged
---

```{r, echo=FALSE}
# Clean up previous executions
targets::tar_destroy("all", ask=FALSE)
```

We create the targets pipeline as normal:

```{r}
targets::tar_script({
  list(
    tar_target(sizes, c(10E6, 10E7, 10E8)),
    tar_target(make_vectors, numeric(sizes), pattern = map(sizes))
  )
}, ask = FALSE)
```

We need to specify a directory that will be used to save the profiling results:
```{r}
monitor_path <- file.path(getwd(), "profile_results")
```

```{r}
#| echo = FALSE
# Clean up previous outputs if they exist
list.files(monitor_path, full.names = TRUE) |> unlink()
```

When it comes to running, we pass in the custom `callr_function`.
In addition, we need to pass that function arguments using `callr_arguments`.
One of these arguments must be `monitor_path`.

```{r}
targets::tar_make(
  callr_function = tarprof::callr_profile,
  callr_arguments = list(
    monitor_path = monitor_path
  )
)
```
Note that for the moment, it is not recommended that you use any parallelism when running the pipeline in profiling mode.
In other words, when calling `crew::crew_controller_local`, use `workers = 1`.
Eventually I hope to lift this limitation.

Once the targets pipeline has finished, we can access the profiling data using `tarprof::profile_data`.
This returns a data frame where each row is one timepoint, and the columns correspond to various process metrics.
```{r}
profile <- tarprof::profile_data(monitor_path)
profile
```

However, this information isn't much help without the knowledge of which targets were run at which times.
We can integrate this information using `tarprof::profile_per_target`:

```{r}
per_target <- tarprof::profile_per_target(profile)
per_target
```

Next, we can use the built-in summary function to get the maximum memory usage and CPU efficiency of each target:
```{r}
profile_summary <- tarprof::summarise_targets(per_target)
profile_summary
```

Finally we can use `tarprof::memory_plot` to represent the memory usage 
In the plot below, each colour corresponds to a different target.
The coloured band indicates the time that `targets` thinks the target was running for (although I'm unsure how accurate this is).
The labelled point indicates the maximum memory usage for that target.
Note that these maximum points correspond to the value of `peak_memory` in the previous data frame.
```{r}
#| fig.height = 6,
#| fig.width = 10
tarprof::memory_plot(profile)
```



